Improvement of crash forces in structures using optimization tools.

### 2016-07-27 paper.tex
Avances

The use of cohesive elements allowed to make the adhesive's mesh much coarser due to their aspect ratios requirements. These elements were created with a size of $\SI{2.0}{\mm}$, and had only one element in the $\SI{0.3}{\mm}$ layer thickness. Other tried element types, specifically solids, had problems if side lengths were bigger than about $\SI{0.5}{\mm}$, and were completely unfeasible with lengths larger than $\SI{1.0}{\mm}$ approximately.

@@

\subsection{Simulation results}

>>>>

The use of cohesive elements allowed to make the adhesive's mesh much coarser due to their aspect ratios requirements. These elements were created with a size of $\SI{2.0}{\mm}$, and had only one element in the $\SI{0.3}{\mm}$ layer thickness. Other tested element types, specifically solids, had problems if side lengths were bigger than about $\SI{0.5}{\mm}$, and were completely unfeasible with lengths larger than $\SI{1.0}{\mm}$ approximately.

@@

\subsection{Simulation results}
subsection{F-D}
\label{sec:F-D}

Typical crash test F-D present a series of alternating peaks and valleys of similar values, except for the first peak, which is greater in value (about twice or three times the mean value) and much more pronounced, as it can be seen on \cref{fig:phdcostas_f-d}. Except in case of critical situations, a clear maximum peak takes place in this first peak.

\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{figures/IMG_CUTRES/phdcostas_f-d}
\caption[Another F-D.]{Another F-D. Taken from \cite{phdCostas}.}
\label{fig:phdcostas_f-d}
\end{figure}

In order to filter high frequency effects, a SAE 600 filter was applied to the simulation results \cite{Huang}. This was also interesting as the level of noise in the output functions made it difficult to distinguish them when plotted together. \Cref{fig:F-D_frictionless,fig:F-D_rough} display modelled crash boxes with frictionless and rough interaction properties respectively. In that same figure and in the upcoming ones, nomenclature is as follows:

\begin{itemize}
	\item ``A'' or ``B'' indicating the cross-section of the tube: ``A'' for the top-hat, and ``B'' for the double hat.

	\item Following that, ``R'', indicating that the rough tangential contact property was used, or ``Fl'', for the frictionless case.

	\item An ``R'' after the underline indicates that the crash box had riveting in the triggered cross section.

	\item ``Sb'' after the underline marks the presence of a stabilizing box in the model.
\end{itemize}

% Insert obtained F-D curve
\begin{figure}
	\centering
	\begin{minipage}[b]{.9\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/AFl}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.9\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/BFl}
	\end{minipage}
	\caption[F-D for modeled cross sections, both top-hat and double hat, with different modeled configurations with frictionless contact.]{F-D for modeled cross sections, both top-hat (red) and double hat (blue), with different modeled configurations with frictionless contact. SEA values in brackets in $\si{\kJ/\kg}$.}
	\label{fig:F-D_frictionless}
\end{figure}

\begin{figure}
	\centering
	\begin{minipage}[b]{.9\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/AR}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.9\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/BR}
	\end{minipage}
	\caption[F-D for modeled cross sections, both top-hat and double hat, with different modeled configurations with rough contact.]{F-D for modeled cross sections, both top-hat (red) and double hat (blue), with different modeled configurations with rough contact. SEA values in brackets in $\si{\kJ/\kg}$.}
	\label{fig:F-D_rough}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{IMG_CUTRES/peroni_qstat_fd}
	\caption[F-D obtained by \cite{Peroni2009} in quasi-static test for studied adhesive and other bonding solution.]{F-D obtained by \cite{Peroni2009} in quasi-static test for studied adhesive (blue) and other bonding solution (gray).}
	\label{fig:peroni_qstat_fd}
\end{figure}

Qualitatively, this curves are very similar to those obtained by \cite{Peroni2009}. \Cref{fig:peroni_qstat_fd} depicts a quasi-static test performed by these authors with the same section and bonding solution. Facing these similitudes, the model is considered valid. Differences are commented on \cref{sec:interpretation}.

In general, a uniform F-D would be the most desirable scenery, as it would imply maximizing the Ea ---which would be equal to the average value multiplied by the total time--- with the minimum Pk. As this is not possible in practice, the best solution will be the one with the most constant-like behavior.

\subsubsection{Mean and standard deviation}

The mean and the SD of F-D are measured in each case. The former one is the least interesting of both, as it is directly related to SEA, which is already being calculated.

However, SD is fair more interesting for the analysis, as it gives an idea of the uniformity of the F-D during the analysis time span. As high values of the transmitted force are origin of injury of the occupants, the most uniform resulting curve will be the one with the lesser values of local peaks for the same mean load, and thus, the more desirable.

\section{Collapse mechanism}

The origin of the mentioned difference between quasi-static and impact results may be related to the collapse mechanism. Specifically, to the rate of changing the response mechanism for the crash box, from in-plane compression of the plates ---which is directly related to Pk---, to the initiation of wave formation. In the developed model, if compared to the collapse images provided by \cite{Scattina2011}, this rate is far slower. The last local peak of the F-D does not take place within the simulation interval due to a longer time span of the main peak.

\subsection{Wave formation}
\label{sec:wave_formation}

Crash box plates bending is the main way of energy absorption through elastic-plastic deformation. Wave formation consists on the formation of a series of foldings along the plates of alternating directionality, so the geometric axis of the tube is approximately kept in place, as it can be seen on \cref{fig:waves}. The non-accomplishment of this last condition is a case of critical situation.

\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{figures/IMG_CUTRES/waves}
\caption[Waves formed on a crushed tube.]{Waves formed on a crushed tube. Taken from \cite{Langseth}.}
\label{fig:waves}
\end{figure}

It is in the wave formation process where another remarkable difference from the models tested by \cite{Scattina2011} takes place. In the present study, although waves develop sequentially as they were expected to, some simultaneity can be perceived on a certain length of the tube in some cases, like the one represented in \cref{fig:wave_form}. This is not considered binding of the validity of the model as, apart from happening on the impact head, wave formation may take also place in the opposite end of the tube or in some mid-point \cite{Abedrabbo2009, Costas2013} in this slender crash devices.

\begin{figure}
	\centering
%	\begin{minipage}[b]{.08\linewidth}
%		\centering
%		\includegraphics[width=\linewidth]{IMG_CUTRES/c0}
%	\end{minipage}
%	\quad
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/c1}
		$\SI{3}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/c2}
		$\SI{6}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/c3}
		$\SI{9}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/c4}
		$\SI{12}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/c5}
		$\SI{15}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/c6}
		$\SI{18}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/c7}
		$\SI{21}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/c8}
		$\SI{24}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/c9}
		$\SI{27}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.15\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/c10}
		$\SI{30}{\ms}$
	\end{minipage}
\caption{Early stages of wave formation process on the impact head.}
\label{fig:wave_form}
\end{figure}

During the development of this study, several adherend thicknesses were tried as a manner of influence on the simultaneity/sequentiality of the wave formation. It was checked that thicker adherends were proner to develop sequentiality in this process, although other problems arise, as it is explained later.

\subsection{Critical situations}
\label{sec:critical_sits}
\cite{Peroni2009} found several situations in impact tests in which the expected collapse mechanism wasn't achieved. Instead, bonding rapidly failed, making almost only use of the plate's capabilities to absorb the impact through its elastic-plastic deformation like bending shells, usually without wave formation at all or only on a part of the tube.

When this situation takes place, Ea may get drastically reduced, depending on several parameters. During the study development, it was found on several unprecise models ---i.e.: with minored adhesive properties--- that this critical situations can drop SEA to a half or even a third of the expected values if compared with non-critical values given by \cite{Peroni2009} on their stable counterparts. In some cases, the general effect of this has less importance, as it will be shown. As previously explained, crash boxes fairly improve their response to this situation by fixing togheter the adherends plates with rivets \cite{Peroni2009}.

Critical situations also take place on FEM models. \cite{Yang2012} found this happening on a double-hat hexagonal tube subjected to impact (\cref{fig:yangs_tube}) using a validated model with equivalent adhesive properties. \cite{Yamashita2013} also found this on impact tests and models of a top-hat tube, being the experimental and the modelled tests very similar in their results.

In this study, they were mainly found on double-hat square tubes, being the top-hat solution fairly more resistant to these problems.
% SELF EXAMPLE AND FIGURE

The importance of controlling this misfunctions also has to do with material efficiency, as the stable collapse mechanism reaches the greatest values of Ea, with a reasonable control of Pk.

In the present study, as previously stated, they were controlled by the addition of a stabilizing box and spot weld points in the flanges at the triggering cross section. Although they are not prevented completely, the general behavior of the tube is fairly improved, as it gets closer to what is expected when comparing to \cite{Peroni2009} and \cite{Scattina2011}.

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{IMG_CUTRES/yangs_tube}
	\caption[FEM analysis of a hexagonal crash box carried out by \cite{Yang2012}.]{FEM analysis of a hexagonal crash box carried out by \cite{Yang2012}. The begginning of tube's head opening can be seen on stage B, and it has totally peeled the adhesive layer by stage C.}
	\label{fig:yangs_tube}
\end{figure}

Using the scripting capabilities of the developed model, an hexagonal crash tube was tested. The collapse process of this section in the developed model is fairly prone to trigger missfunction, and it highly resembled the problems that \cite{Yang2012} found in the simulation.

% Insert figure & comment

This section aims to expose some of the most common critical situations found during the study development, usually by changing the boundary conditions affecting the tube. The reasons involved in this malfunctioning are related and always present combined, and were subducted by the addition of rivets and a stabilizing box to the model (\cref{sec:impact}).

\subsubsection{Triggering missfunctions}  % Head aperture
\label{sec:trig_missf}

Without the eventually included rivets, depending on the adherend thickness ---specifically for low values of this parameter---, triggering could not work properly: an excesive bending takes place at that point in the bonding flanges, together with little bending on points close to that part of the tube. In addition, this deformations happen to lead to opening the section.

This aperture may be caused either by a tendency to form waves with stiffer ---due to their undeformed state--- sections next to it which restrain this collapse mechanism on that point, or either by the presence of symmetrical wave patterns instead of parallel wave patterns leading to a wave in each adherend trying to open the section next to the trigger. Both situations may coexist, but either of them provokes the adhesive failure by pure mode I loading.

Failure may happen on the triggered cross section (see \cref{fig:trig_misf_A}, in this study, this was solved by using spot weld points in that cross section) or on the mid-tube (see \cref{fig:trig_misf_mid}). In this last case, general bending may also take place afterwards.

\begin{figure}
	\centering
	\begin{minipage}[b]{.65\linewidth}
		\includegraphics[width=\linewidth]{IMG_CUTRES/trig_misf_A1}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.65\linewidth}
		\includegraphics[width=\linewidth]{IMG_CUTRES/trig_misf_A2}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.65\linewidth}
		\includegraphics[width=\linewidth]{IMG_CUTRES/trig_misf_A3}
	\end{minipage}
	\caption{Trigger misfunction development on a top-hat section crash tube at $\SI{1.5}{\ms}$, $\SI{4.5}{\ms}$ and $\SI{15}{\ms}$.}
	\label{fig:trig_misf_A}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{IMG_CUTRES/trig_misf_mid}
	\caption[View cut detail of a double hat section crash tube with triggering misfunction initiation on a middle point.]{View cut detail of a double hat section crash tube with triggering misfunction initiation on a middle point. Focus on the symmetrical bending wave pattern. Adhesive in blue.}
	\label{fig:trig_misf_mid}
\end{figure}

%\begin{figure}
%	\centering
%	\includegraphics[width=.7\linewidth]{IMG_CUTRES/tmfB_detail}
%	\caption{Detail of a double hat section tube head in which triggering missfunction is starting to develop.}
%	\label{fig:tmfB_detail}
%\end{figure}

\begin{figure}
	\centering
	\begin{minipage}[b]{.22\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/tmf1}
		$\SI{0.6}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.22\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/tmf2}
		$\SI{1.05}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.22\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/tmf3}
		$\SI{1.5}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.22\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/tmf4}
		$\SI{1.95}{\ms}$
	\end{minipage}
	\caption[Triggering missfunction development process on a double hat section crash tube.]{Triggering missfunction development process on a double hat section crash tube. Adhesive in blue.}
	\label{fig:tmf}
\end{figure}

By facing \cref{fig:tmf}, it is supposed that this situation has its origin on an adherend thickness-triggering relation that also depends on the cross section of the tube, as the plates initial bend is allowed by the reduced adherend thickness and this is the origin of the peeling failure due to the plates bending directionality, which tends to open the union from the inside. After this situation has started, the more the head is deformed, the more it is developed. There are several other arguments supporting this theory:
\begin{itemize}
	\item The lack of triggering also leads to this situation.

	\item Hexagonal cross sections \cite{Yang2012} are particulary prone to develop this critical situation.

	\item Thicker adherends seem to be about of avoiding this misfunction before starting other critical collapse mechanisms.

	\item It is the main critical situation that can be found on top-hat cross section crash tubes.
\end{itemize}

\Cref{fig:tmf_fd} shows the corresponding force-displacement curve of the tube of \cref{fig:tmf}. In this critical situation, adherends start to bend over a certain point of the tube provoking the peeling along the tube in the process. The second peak present in \cref{fig:tmf_fd} may be motivated by the impact plate reaching this bending point and thus starting an in-plane compression of the adherends like the experienced in the beginning.

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{IMG_CUTRES/tmf_fd}
	\caption{Force-displacement curve for a crash tube with triggering missfunction.}
	\label{fig:tmf_fd}
\end{figure}

This misfunction is also particularly independent of the tube length, as the analysis with different values of this parameter showed. This situation is also particularly easy to be developed on hexagonal crash boxes, as \cref{fig:hex_tmf} shows.

\begin{figure}
	\centering
	\begin{minipage}[b]{.3\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/hex1}
		$\SI{0.6}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.3\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/hex2}
		$\SI{1.2}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{.3\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/hex3}
		$\SI{1.8}{\ms}$
	\end{minipage}
	\caption[Triggering missfunction development process on a hexagonal cross section crash tube.]{Triggering missfunction development process on a hexagonal cross section crash tube. Adhesive in blue.}
	\label{fig:hex_tmf}
\end{figure}

\subsubsection{General bending}

It was found that in many cases, during the wave formation process, a minor difference between plates deformation, eventually resulted in the box bending by some mid-point, diverting the tube's directrix instead of crushing the device in a straight direction (see \cref{fig:general_bending}).

\begin{figure}
	\centering
	\begin{minipage}[b]{.7\linewidth}
		\includegraphics[width=\linewidth]{IMG_CUTRES/general_bending_73}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.3\linewidth}
		\includegraphics[width=\linewidth]{IMG_CUTRES/general_bending_48}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.3\linewidth}
		\includegraphics[width=\linewidth]{IMG_CUTRES/general_bending_72}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.3\linewidth}
		\includegraphics[width=\linewidth]{IMG_CUTRES/general_bending_55}
	\end{minipage}
\caption[Final deformation status of a double hat section crash tube model without stabilizing box in a general bending critical situation.]{Final deformation status of a double hat section crash tube model without stabilizing box in a general bending critical situation. Crushing from the left.}
\label{fig:general_bending}
\end{figure}

Analyzing the origin of this situation, several possible reasons were considered:
\begin{itemize}
	\item A longer wave on one side, followed by a less pronounced one. Membrane effect on the former one makes it a stiffer point. The last one is a weak section, as the consecutive adherend planes are folding together. As this situation only takes place on one of the adherends, the faux-symmetry ceases to exist, thus bending the tube by some mid-point.

	\item Following a behaviour similar to that one found in triggering missfunction, aperture of the section happens in some mid-point. Usually an excesively opened wave by the union plane, sided by two under-formated waves that cannot compensate the aperture, triggers this failure.
\end{itemize}

This situation usually takes place with minor adhesive failure on its initial phases, and rapidly failing in a peel-shear combination when the bend is completely formed on almost the whole surface.

Ideal bonding ---using tie constraints instead of a material union--- presented this collapse mechanism, only differing in the last phases, depicted in \cref{fig:general_bending}, in which the adhesive fails.

This suggests that the adhesive meets its objective on retainning the two flanges together, at least until the critical failure has completely developed itself, and thus suggesting an adherend or trigger origin of this problem.

It also suggests that the adhesive influence on the general response is of little importance on the last phases, meaning that once the critical situation is initiated, the response barely depends on the bond.

On the other hand, top-hat section crash tubes were found to be fairly more resistant to developing this kind of malfunction, as no cases were found.

\subsubsection{General peeling due to plates buckling}

Excessively thick adherend plates prevent wave formation, resulting in other collapse mechanisms development, such as a buckling-like deformation, as a slender beam subjected to high compression. In this situation, each plate bends to a side, peeling the union in the process. In this situation, the stiffness difference between adherend and adhesive results in a behavior that could be described as if the former imposed deformations to the later.

Although it could not be measured, it is supposed that a big share part of the Ea value comes from elastic-plastic deformation of the adherend plates. The adhesive failure is purely mode I, and thus only the corresponding fracture energy is absorbed, which is recalled that was about one fifth of the other modes value. In spite of that, SEA values with $\SI{2}{\mm}$ plate thickness were close to the ones found with $\SI{1}{\mm}$ carried out by \cite{Peroni2009} with a stable collapse mechanism.

\begin{figure}
	\centering
	\begin{minipage}[b]{.48\linewidth}
	\centering
	\begin{minipage}[b]{\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/gppb67}
		$\SI{2.0}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/gppb84}
		$\SI{2.5}{\ms}$
	\end{minipage}
	\quad
	\begin{minipage}[b]{\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/gppb100}
		$\SI{3.0}{\ms}$
	\end{minipage}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.48\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/gppb300}
		$\SI{9.0}{\ms}$
	\end{minipage}

	\caption{General peeling due to plates buckling collapse process.}
	\label{fig:gppb}
\end{figure}

This fact may be used as an argument to make the adherends thicker, but the Pk was also strongly increased to over $\SI{100}{\kN}$ in this case as it can be seen on \cref{fig:gppb_fd}, which is undesirable. In that same figure, it can be seen how the pure mode I failure of the whole adhesive allows little energy absorption. SEA is $\SI{4.28}{\kJ/\kg}$, lower than other solutions due to this inefficiency.

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{IMG_CUTRES/gppb_fd}
	\caption{F-D for a $\SI{2}{\mm}$ adherend thick in which general peeling due to plates buckling is developed.}
	\label{fig:gppb_fd}
\end{figure}

Unlike the commented triggering missfunction, general peeling finds its origin on a buckling-like behavior of the plates which produces the peeling, while the malfunction of the trigger leads to local failure of the bonding, leading to the rotation of a part of the plate around a wave formed in a rearer point of the tube. In addition, triggering missfunction is easier to develop with lower thickness values, while general peeling is produced with higher values of this parameter.

\section{Interpretation}  % Include different geoms comparation if possible
\label{sec:interpretation}

In general terms, top-hat section tubes better resemble the reference crash boxes, specially due to their higher resistance to develop undesired collapse mechanisms.

\subsection{Stable collapse mechanism}

\Cref{fig:stable} depicts the collapse sequence of a top-hat crash tube, showing a stable crushing pattern. Analyzing the modeling, it can be concluded that this collapse was achieved thanks the stabilizing box, as it retains the plates at certain points. \Cref{fig:stabil_box} depicts the final state of the crushing process, showing how the stabilization box retained the crash tube.

\begin{figure}
	\centering
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a0}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a1}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a2}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a3}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a4}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a5}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a6}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a7}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a8}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a9}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.06\linewidth}
		\centering
		\includegraphics[width=\linewidth]{IMG_CUTRES/a10}
	\end{minipage}

	\caption[Stable collapse mechanism achieved in the top-hat tube with stabilizing box.]{Stable collapse mechanism achieved in the top-hat tube with stabilizing box. Semi-transparent projection with adhesive in red. Total time: $\SI{15}{\ms}$; uniform spacing.}
	\label{fig:stable}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=.7\linewidth]{IMG_CUTRES/parallel_stable}
	\caption{Final state on parallel projection with the stabilizing box represented.}
	\label{fig:stabil_box}
\end{figure}

Reaction force is analyzed in this case in order to check the importance share of the stabilizing box on achieving this result. Its F-D is displayed in \cref{fig:stabil_F}, with an equivalent SEA of $\SI{0.30}{\kJ/\kg}$ and peaks of up to $\SI{4.4}{\kN}$. This force has one only component, parallel to the Y axis, which is reminded to be normal to the crushing direction and to the bonding flanges.

\begin{figure}
	\centering
	\includegraphics[width=.7\linewidth]{IMG_CUTRES/RF2_stable}
	\caption{Reaction force on the stabilizing box.}
	\label{fig:stabil_F}
\end{figure}

According to the results displayed on \cref{fig:stable,fig:stabil_box,fig:stabil_F}, it can be concluded that the stabilizing box helps on providing an stable collapse mechanism to the crash tube through the inclusion of a certain force with a minimum SEA input to the system.

\subsection{Factors on absorption of energy}
\label{sec:Ea_factors}

Facing the F-D and different collapse states at several time intervals, an analysis on the relative importance of each factor on Ea is carried out.

The in-plane compression of the rear un-collapsed part of the tube, together with plastic deformation of the frontal end, are the main actors on the base reaction force ---a minimum maintained level that keeps its value almost constant and leaving the variable part to other factors.

Bending waves \textit{per se} do not have great influence on the peaks and valleys series of the F-D, but the adhesive failure pattern does, and it is determined by the former. This means that it is not the adherend plastic deformation the main factor of this variable part, although it has certain variability. \Cref{fig:ads_collapse_progresion} is the case in which this phenomenon can be most easily perceived, as in certain moment, adhesive rapidly fails with very little adherend deformation, and highly increasing the reaction force.

In that same figure, the peak between $\SI{8.25}{\ms}$ and $\SI{10.2}{\ms}$ corresponds to some adhesive final failure (depicted by element removal in the first and second states). The same applies more drastically between the third and fourth states, depicting $\SI{13.2}{\ms}$ and $\SI{15.0}{\ms}$ respectively.

This analysis can be carried out for any other case, with the same conclusions, although this one is the most graphical and the easiest one to be percerived.

\begin{figure}
	\centering
	\begin{minipage}[b]{.35\linewidth}
		\centering
		\begin{minipage}[b]{\linewidth}
		\includegraphics[width=\linewidth]{IMG_CUTRES/AR_RSB_8-25}
		\end{minipage}
		\quad
		\begin{minipage}[b]{\linewidth}
		\includegraphics[width=\linewidth]{IMG_CUTRES/AR_RSb_10-2}
		\end{minipage}
		\quad
		\begin{minipage}[b]{\linewidth}
		\includegraphics[width=\linewidth]{IMG_CUTRES/AR_RSb_13-2}
		\end{minipage}
		\quad
		\begin{minipage}[b]{\linewidth}
		\includegraphics[width=\linewidth]{IMG_CUTRES/AR_RSb_15}
		\end{minipage}
	\end{minipage}
	\quad
	\begin{minipage}[b]{.6\linewidth}
		\includegraphics[width=\linewidth]{IMG_CUTRES/AR_RSb}
	\end{minipage}
\caption[Adhesive collapse influence on F-D.]{Adhesive collapse influence on F-D. Collapse states with semi-transparent adherends and adhesive in red at $\SI{8.25}{\ms}$, $\SI{10.2}{\ms}$, $\SI{13.2}{\ms}$, and $\SI{15.0}{\ms}$; and corresponding F-D. In this case, collapse is started by a mid-point.}
\label{fig:ads_collapse_progresion}
\end{figure}

The possible critical situations that can be developed as a collapse mechanism have varying importance on the final results, strongly depending on the cross section. As commented on \cref{sec:critical_sits}, top-hat section presents minor SEA losses and is more resistant to developing this missfunctions, unlike double hat section.

As of this, it can be concluded that there are three main factors influencing on the value of Ea, being these, in order of importance:
\begin{itemize}
	\item Adherend properties: more specifically its geometry and material.
	\item Adhesive characteristics: specially those involved in its failure, like the fracture energy.
	\item Missfunctional behaviour: although in some cases may be negligible, in others it can be determining.
\end{itemize}

Finally, \cref{tab:sea} summarizes the different obtained SEA values. From there, it can be seen how the top-hat section is not affected in the same magnitude in the final SEA value as the double hat section, although the collapse mechanism may change by transferring the wave formation process to other part of the tube and certain other corresponding implications. The obtained values are close to those experimentally obtained by \cite{Peroni2009}, giving certain credit on the goodness of the results of the present study.

On the other hand, the double hat section SEA obtained values drastically change when modifying the contact interaction properties, dropping to between $82\%$ and $63\%$ of values with other interaction definition, and about a half or even a third of the experimental values obtained by \cite{Peroni2009}. The rough case with stabilization box seems to get the closest to resembling cited experiments, although its collapse mechanism is not the same, as the modeled one generates waves in the mid-tube, as can be seen on \cref{fig:best_B_tube}

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{IMG_CUTRES/best_B_tube}
	\caption[Collapse of the double hat section tube with stabilization box and rough contact property.]{Collapse of the double hat section tube with stabilization box and rough contact property. Adhesive in blue. SEA: $\SI{7.34}{\kJ/\kg}$.}
	\label{fig:best_B_tube}
\end{figure}

% \begin{table}[htpb]
% 	\centering
% 	\begin{tabular}{llcc}
% 		\hline
% 		\multirow{2}{*}{Contact} & \multirow{2}{*}{Situation} & \multicolumn{2}{c}{Cross section} \\ \cmidrule{3-4}
% 		\multicolumn{2}{l}{}                                    & Top-hat         & Double hat     \\ \hline
% 		\multirow{4}{*}{Rough}                  & -             & $5.43$          & $5.20$         \\
% 		& R             & $5.36$          & $6.08$          \\
% 		& Sb            & $5.70$          & $7.34$          \\
% 		& RSb           & $5.61$          & $6.69$          \\ \hline
% 		\multirow{4}{*}{Frictionless}           & -             & $4.21$          & $3.32$         \\
% 		& R             & $5.50$          & $3.86$         \\
% 		& Sb            & $5.55$          & $5.88$          \\
% 		& RSb           & $5.40$          & $5.51$          \\ \hline
% 	\end{tabular}
% 	\caption[SEA summary.]{SEA summary. ``R'' stands for riveted tube; ``Sb'', for tube with stabilizing box; ``RSb'', for both simultaneously.}
% 	\label{tab:sea}
% \end{table}

\subsection{On load standard deviation}

Facing the factors that were concluded on \cref{sec:Ea_factors}, the SD value of the F-D can be interpreted also as a measure of the progressiveness or the suddenness of the failure of the crash box, specially and more specifically of the adhesive.

% \begin{table}[htpb]
% 	\centering
% 	\begin{tabular}{llcc}
% 		\hline
% 		\multirow{2}{*}{Contact} & \multirow{2}{*}{Situation} & \multicolumn{2}{c}{Cross section} \\ \cmidrule{3-4}
% 		\multicolumn{2}{l}{}                                    & Top-hat         & Double hat      \\ \hline
% 		\multirow{4}{*}{Rough}                  & -             & $6.79$          & $10.47$         \\
% 		& R             & $6.60$          & $8.84$          \\
% 		& Sb            & $8.04$          & $6.80$          \\
% 		& RSb           & $7.25$          & $7.73$          \\ \hline
% 		\multirow{4}{*}{Frictionless}           & -             & $5.76$          & $11.91$         \\
% 		& R             & $5.53$          & $10.72$         \\
% 		& Sb            & $5.29$          & $8.65$          \\
% 		& RSb           & $4.97$          & $8.82$          \\ \hline
% 	\end{tabular}
% 	\caption[SD summary.]{SD summary. ``R'' stands for riveted tube; ``Sb'', for tube with stabilizing box; ``RSb'', for both simultaneously.}
% 	\label{tab:standard_dev}
% \end{table}

In general terms, top-hat section shows a better performance in terms of SD, as it can be seen on \cref{tab:standard_dev}, likely thanks to its better resistance to developing critical situations. Both rough cases with stabilizing box on rough contact conditions seem to be the exception to the tendency, as the top-hat tube shows a larger SD than the double hat one. Their F-D is depicted in \cref{fig:R_Sb}. A similar phenomenon happens on those cases that add rivets to these ones, although not in an enough magnitude to make the double hat section value bigger than the top-hat section one.

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{IMG_CUTRES/R_Sb}
	\caption{F-D of models with rough contact and stabilizing box.}
	\label{fig:R_Sb}
\end{figure}

Although none of these cases depicts a critical situation, they behave differently to other similar tests. Analyzing the collapse mechanism in the top-hat section, the rapid mode II failure at certain stages creates local peaks also explained in \cref{sec:final_tendency} that are related to the variability of the F-D.

Concurring with this situation, on the other hand, the double hat section shows in these cases some of the most stable collapses among the obtained results, allowing thus a more balanced result against its counterpart. In spite of being fairly stable, its SD is still particularly high if compared to many top-hat section results. Analyzing the F-D, the peaks and valleys series is included in a general downwards tendency, unlike other series which oscillate among a fairly constant level. This implies that SD is not the perfect tool for measuring the stability of the collapse mechanism, although it is good enough to give an idea.

Double hat section on frictionless contact conditions, whose F-D are represented in \cref{fig:F-D_frictionless}, present the greatest values of SD among the modeled tubes. In spite of the similarities between these curves, the showed collapse mechanism is different between those with and without stabilizing box, although the causes are fairly the same: a great valley after the Pk followed by a second local peak around $\num{8}\sim\SI{10}{\ms}$.

The cases without stabilizing box find the genesis of this late peak in the developed critical situation, which corresponds to a general bending case. As \cref{fig:gen_bend_weakening} shows, the peak implies the final dispossure of Ea by the frontal part of the tube, as it completely bends over itself. Beyond this point, this frontal part does not intervene any more, and the collapse starts again in some way from this moment only using the capabilities of the rest of the tube.
